Data Preparation

### 2019-01-09 Data Preparation.Rmd
transcripts: identifies useless variables and saves them as a vector.

###Identifying usless variables
Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage

>>>>

###Identifying usless variables
Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
```{r}
not_keep <- c("Booking Status",
              "Appraisal Status Description",
              "Credit Type",
              "Personnel Number",
              "Event Object Id",     
              "Business Event Abbreviation",               
              "Event Description",                   
              "Start time",                         
              "End time",                            
              "Date",                               
              "Studyplan",                           
              "Conditional booking",                 
              "Wachtlist",                           
              "Object ID", #? has values e.g. 50236380                        
              "Object Name",  #?  has values, e.g. "BE-Universitair Ziekenhuis Brussel"
              "Start Date",   #? has values, e.g.  "12/16/13"                     
              "End Date",     #? has values, e.g. "5/14/10"                      
              "Number of Weeks", 
              "Name (Employee/Applicant)",
              "Appraiser ID",      #HAS VALUES BUT NOT IMPORTANT, e.g. 70011933
              "Appraiser Name",    #HAS VALUES BUT NOT IMPORTANT, e.g.  J.J. Briede  
              "Academic Work ID",  #has values, eg.53EA405080711826E10000008978030A
              "Attempted Credits", #HAS VALUES BUT NOT IMPORTANT
              "Earned Credit",
              "Individual Work",
              "Appraisal Status",
              "Booking Reason",
              "Appraisal Date" #day when grades were put in
              ) 
```
